---
title: "About data science."
format: html
editor: visual
---

# STEP3

## First.

1.  What do you think being a data scientist is about?

-   I work as IT staff of financial company in Korea. Based on my current role, being a data scientist is about supporting a company's decision-making. A data scientist should deal with a lot of information (data) to find important clues. They use these clues to help a company make good decisions.

2.  What differences/similarities do you see between data scientists and statisticians?

-   **Similarities:** Both data scientists and statisticians are very good with numbers and data. They both work with data to find answers.
-   **Differences:** I think their main goal is different.
    -   **Statisticians** use very careful math and theory to explain why something happened. They focus more on theory than practical application.
    -   **Data scientists** are more like **builders**. They use data to build a product or a tool. For example, they build the system that recommends videos on YouTube. They care most about making good predictions that are useful.

3.  How do you view yourself in relation to these two areas?

    With my background in Computer Science, my current IT role connects directly to **data science**. I build and develop our company's systems, which requires applying data-driven solutions to real-world problems.

    However, as I move into a management position, my responsibilities will shift. I will need to make major strategic decisions for our IT and financial direction. To do that effectively, my decisions must be grounded in **statistics**, making that field increasingly important for my career.

## Second.

```{r}
y <- density(iris$Petal.Width)
```

R code chunk to determine the class, type, and structure of the object y.

```{r}
class(y)
typeof(y)
str(y)
```

R code chunk that uses the plot function on y.

```{r}
#| echo: FALSE
plot(y, main = "Density of Iris Petal Width")
```
